Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-31 paper/paper_new.tex
Updates from Overleaf

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{NSF Grant ???} }}
%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., e.g., bgnn, and even mention of metadata research center. 
%for the record: Research supported by NSF OAC #1940233 and #1940322.

@@

This limitation is magnified, when trying get a handle on the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, but metadata properties used to record image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bio-generated neural network.
%will add cites above, depending on paper length.

@@

\subsection{Automatic Metadata Generation}
Metadata researchers are aware of challenges posted by manual metadata generation, both in terms of time,  //Technical metadata capturing image lighting, camera, date of digitization and other information are automatically generated, but 
%jane working here, i figured out how to scope this, I think! I need to get outside now, but back later.

>>>>

\title{Automated Metadata Generation for Fish Specimen Image Collections%*\\
    {\footnotesize \thanks{NSF Grant ???} }}
%do we add grant now, or wait til acceptance. i think we need to ultimately remove any identifying info., i think bgnn is likely okay; but, perhaps mention metadata research center (MRC) need to be removed?. if so, i kind of like to put it back in for final version, if accepted. it helps with getting funding ... you are both listed on the MRC page. we should check on the identifying info. removed, or not.
%for the record: Research supported by NSF OAC #1940233 and #1940322.

@@

This limitation is magnified when trying get a handle on the actual quality of the digitized specimen. Descriptive oriented standards support search and retrieval, and the biodiversity community advocated for data fitness standards \cite{chapman2020developing}. Even so, metadata properties used to record image quality is severely limited and generally missing. This point is addressed in detail in \cite{leipzig2021biodiversity}, justifying the capture of 22 metadata properties supporting selection of high quality images for the development of a bgnn. Although, the manual generation of this metadata is costly in terms of labor and time.
%will add cites above, depending on paper length.

@@

\subsection{Automatic Metadata Generation}
Technical metadata, such as camera settings and temporal information (date and time) are automatically generated during a digitization sequence, following standards such as XX. Some of this metadata may be useful in for selecting a machine learning sample. A researcher may desire images captured chiefly with a certain aperture setting. Even so, the majority of automatically captured technical metadata associated with digitized specimens is insufficient for computational research, leaving researchers to reply on manually generated descriptive metadata, which itself is sparse.

Automatic metadata generation of descriptive bibliographic data has been a research focus for close to 20 years \cite{liddy2002automatic,greenberg2004metadata,cardinaels2005automating}. Researchers have applied support vector machine (SVM) approaches \cite{han2003automatic}, and associated networks to address sparse and incomplete metadata \cite{rodriguez2009automatic}, and various successes are integrated into day-to-day workflows.

%\cite{heidorn2008automatic} speciment labels \cite{manso2004automatic} carteogrpahic info.
